Supplement A to 'Researchers understand and use the logic of significance testing in a novel statistical reasoning task

### 2022-11-30 inst/manuscript/supplementA.Rmd
fixed vignette issues that kept package from installing

dat %>%
    mutate(effect_size = abs(effect_size),
           `# strong` = factor(n_strong)) %>%
    group_by(effect_size, true_winner, response, `# strong`) %>%
    tally() %>%
    complete(effect_size, true_winner, response, `# strong`, fill = list(n = 0)) %>%
    ungroup() %>%
    filter(response != "bored") %>%
    mutate(
      dec_type = case_when(
        true_winner != "null" &
          true_winner != response &
          response %in% c("jinglies", "sparklies") ~ "sign_error",
        response %in% c("jinglies", "sparklies") ~ "report_difference",
        response == "same" ~ "same",
        response == "no_detect" ~ "no_detect"
      )
    ) %>%
    group_by(dec_type, effect_size, `# strong`) %>%
    tally( wt = n ) %>%
    complete(dec_type, effect_size, `# strong`, fill = list(n = 0)) %>%
    group_by(effect_size, `# strong`) %>%
    mutate(total = sum(n)) %>%
  filter(dec_type == "report_difference") %>%
  mutate(
      p = n / total,
      stderr = sqrt(p * (1 - p) / total),
      lo = qlogis(p),
      lo.stderr = stderr / dlogis(qlogis(p))
    ) %>%
  select(-dec_type) %>% 
  ggplot(aes(x = effect_size, y = p, group = `# strong`)) +
      geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = 0,
      ymax = 1,
      color = NA,
      fill = "#EEEEEE",
      alpha = .1
    ) +
    geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = .8,
      ymax = 1,
      color = NA,
      fill = "#DDDDDD",
      alpha = .1
    ) +
    geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = 0,
      ymax = .2,
      color = NA,
      fill = "#DDDDDD",
      alpha = .1
    ) +
    geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = .95,
      ymax = 1,
      color = NA,
      fill = "#CCCCCC",
      alpha = .1
    ) +
    geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = 0,
      ymax = .05,
      color = NA,
      fill = "#CCCCCC",
      alpha = .1
    ) +
    geom_segment(aes(
      x = 0,
      y = 0,
      xend = 0,
      yend = 1
    )) +
    geom_hline(yintercept = c(0, 1)) +
    geom_line(aes(linetype = `# strong`, col = `# strong`), size = .7) +
    geom_point(aes(col = `# strong`)) +
    geom_ribbon(aes(
      ymin = p - stderr,
      ymax = p + stderr,
      fill = `# strong`
    ),
    alpha = 0.2) +
      xlab("Effect size") + ylab("Proportion of responses") +
    coord_cartesian(
      ylim = c(0, 1.2),
      xlim = c(0, 1),
      expand = FALSE,
      clip = "off"
    ) +
    scale_y_continuous(breaks = seq(0, 1, .1)) +
    scale_x_continuous(breaks = seq(0, 1, .2)) +
    theme(
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank(),
      panel.background = element_blank(),
      text = element_text(
        family = MoreyHoekstra2019::pkg_options("ggplot_family")
        )
    )

>>>>

dat %>%
    mutate(effect_size = abs(effect_size),
           `# strong` = factor(n_strong)) %>%
    group_by(effect_size, true_winner, response, `# strong`) %>%
    tally() %>%
    ungroup() %>%
    complete(effect_size, true_winner, response, `# strong`, fill = list(n = 0)) %>%
    ungroup() %>%
    filter(response != "bored") %>%
    mutate(
      dec_type = case_when(
        true_winner != "null" &
          true_winner != response &
          response %in% c("jinglies", "sparklies") ~ "sign_error",
        response %in% c("jinglies", "sparklies") ~ "report_difference",
        response == "same" ~ "same",
        response == "no_detect" ~ "no_detect"
      )
    ) %>%
    group_by(dec_type, effect_size, `# strong`) %>%
    tally( wt = n ) %>%
    ungroup() %>%
    complete(dec_type, effect_size, `# strong`, fill = list(n = 0)) %>%
    group_by(effect_size, `# strong`) %>%
    mutate(total = sum(n)) %>%
  filter(dec_type == "report_difference") %>%
  mutate(
      p = n / total,
      stderr = sqrt(p * (1 - p) / total),
      lo = qlogis(p),
      lo.stderr = stderr / dlogis(qlogis(p))
    ) %>%
  select(-dec_type) %>% 
  ggplot(aes(x = effect_size, y = p, group = `# strong`)) +
      geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = 0,
      ymax = 1,
      color = NA,
      fill = "#EEEEEE",
      alpha = .1
    ) +
    geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = .8,
      ymax = 1,
      color = NA,
      fill = "#DDDDDD",
      alpha = .1
    ) +
    geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = 0,
      ymax = .2,
      color = NA,
      fill = "#DDDDDD",
      alpha = .1
    ) +
    geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = .95,
      ymax = 1,
      color = NA,
      fill = "#CCCCCC",
      alpha = .1
    ) +
    geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = 0,
      ymax = .05,
      color = NA,
      fill = "#CCCCCC",
      alpha = .1
    ) +
    geom_segment(aes(
      x = 0,
      y = 0,
      xend = 0,
      yend = 1
    )) +
    geom_hline(yintercept = c(0, 1)) +
    geom_line(aes(linetype = `# strong`, col = `# strong`), size = .7) +
    geom_point(aes(col = `# strong`)) +
    geom_ribbon(aes(
      ymin = p - stderr,
      ymax = p + stderr,
      fill = `# strong`
    ),
    alpha = 0.2) +
      xlab("Effect size") + ylab("Proportion of responses") +
    coord_cartesian(
      ylim = c(0, 1.2),
      xlim = c(0, 1),
      expand = FALSE,
      clip = "off"
    ) +
    scale_y_continuous(breaks = seq(0, 1, .1)) +
    scale_x_continuous(breaks = seq(0, 1, .2)) +
    theme(
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank(),
      panel.background = element_blank(),
      text = element_text(
        family = MoreyHoekstra2019::pkg_options("ggplot_family")
        )
    )
